Offshore Modeling - Manuscript Model

### 2020-02-18 2019_edits/R/offshore_analyses/final_analyses/Manuscript_Offshore_Modeling.Rmd
tilted axis labels

```{r, fig.height=4}

@@

```{r, fig.height=4}
west_foa <- round(mean(seamap_west$crab_presence, na.rm = TRUE), 3)

@@

```{r west fig, fig.height=4}

@@

```{r full fig, fig.height=4}

# Plot
rs_plot_3 <- rs_summary_full %>% 
  ggplot(aes(region, `Mean Catch`, fill = Season)) +
    geom_col(position = "dodge") +
    geom_errorbar(aes(ymin = catch_ymin,
                      ymax = catch_ymax),
                  position = "dodge", 
                  size = .25) +
  scale_fill_manual(name = "", values = setNames(c("gray35", "gray70"), c("Summer", "Fall"))) +
  labs(x = NULL,
       y = expression(paste("Mean CPUE (crabs ", ha^{-1},")"))) + 
  theme(
    legend.position = c(1, .95),
    legend.justification = c("right", "top"),
    legend.box.just = "right",
    legend.margin = margin(0, 6, 2, 2))

@@

```{r west foa, fig.height=4}
rs_plot_2 <- rs_foa %>% 
  ggplot(aes(region, avg_percent_occurrence, fill = Season)) +
    geom_col(position = "dodge") +
    geom_errorbar(aes(ymin = occurrence_ymin,
                      ymax = occurrence_ymax),
                  position = "dodge",
                  size = .25) +
  scale_fill_manual(name = "", values = setNames(c("gray35", "gray70"), c("Summer", "Fall"))) +
  scale_y_continuous(labels = scales::percent, limits = c(0,1)) + 
  labs(x = NULL,
       y = "Percent occurrence") + 
  theme(
    legend.position = c(1, .95),
    legend.justification = c("right", "top"),
    legend.box.just = "right",
    legend.margin = margin(0, 6, 2, 2))

@@

```{r full foa, fig.height=4}
rs_plot_4 <- rs_foa_full %>% 
  ggplot(aes(region, avg_percent_occurrence, fill = Season)) +
    geom_col(position = "dodge") +
    geom_errorbar(aes(ymin = occurrence_ymin,
                      ymax = occurrence_ymax),
                  position = "dodge",
                  size = .25) +
  scale_fill_manual(name = "", values = setNames(c("gray35", "gray70"), c("Summer", "Fall"))) +
  scale_y_continuous(labels = scales::percent, limits = c(0,1)) + 
  labs(x = NULL,
       y = "Percent occurrence") + 
  theme(
    legend.position = c(1, .95),
    legend.justification = c("right", "top"),
    legend.box.just = "right",
    legend.margin = margin(0, 6, 2, 2))

@@

```{r fig.height=4}
rs_plot <- rs_plot + theme(legend.position = "none")
rs_plot + rs_plot_2

>>>>

```{r, fig.height = 4}

@@

```{r, fig.height = 4}
west_foa <- round(mean(seamap_west$crab_presence, na.rm = TRUE), 3)

@@

```{r west fig, fig.height = 4, eval = F}

@@

```{r full fig, fig.height = 4}

# Plot
rs_plot_3 <- rs_summary_full %>% 
  ggplot(aes(region, `Mean Catch`, fill = Season)) +
    geom_col(position = "dodge") +
    geom_errorbar(aes(ymin = catch_ymin,
                      ymax = catch_ymax),
                  position = "dodge", 
                  size = .25) +
  scale_fill_manual(name = "", values = setNames(c("gray35", "gray70"), c("Summer", "Fall"))) +
  labs(x = NULL,
       y = expression(paste("Mean CPUE (crabs ", ha^{-1},")"))) + 
  theme(
    legend.position = c(1, .95),
    legend.justification = c("right", "top"),
    legend.box.just = "right",
    legend.margin = margin(0, 6, 2, 2),
    axis.text.x = element_text(angle = 45, hjust = 1, vjust = .8))

@@

```{r west foa, fig.height = 4, eval = F}
rs_plot_2 <- rs_foa %>% 
  ggplot(aes(region, avg_percent_occurrence, fill = Season)) +
    geom_col(position = "dodge") +
    geom_errorbar(aes(ymin = occurrence_ymin,
                      ymax = occurrence_ymax),
                  position = "dodge",
                  size = .25) +
  scale_fill_manual(name = "", values = setNames(c("gray35", "gray70"), c("Summer", "Fall"))) +
  scale_y_continuous(labels = scales::percent, limits = c(0,1)) + 
  labs(x = NULL,
       y = "Percent occurrence") + 
  theme(
    legend.position = c(1, .95),
    legend.justification = c("right", "top"),
    legend.box.just = "right",
    legend.margin = margin(0, 6, 2, 2))

@@

```{r full foa, fig.height = 4}
rs_plot_4 <- rs_foa_full %>% 
  ggplot(aes(region, avg_percent_occurrence, fill = Season)) +
    geom_col(position = "dodge") +
    geom_errorbar(aes(ymin = occurrence_ymin,
                      ymax = occurrence_ymax),
                  position = "dodge",
                  size = .25) +
  scale_fill_manual(name = "", values = setNames(c("gray35", "gray70"), c("Summer", "Fall"))) +
  scale_y_continuous(labels = scales::percent, limits = c(0,1)) + 
  labs(x = NULL,
       y = "Percent occurrence") + 
  theme(
    legend.position = c(1, .95),
    legend.justification = c("right", "top"),
    legend.box.just = "right",
    legend.margin = margin(0, 6, 2, 2),
    axis.text.x = element_text(angle = 45, hjust = 1, vjust = .8))

@@

```{r fig.height = 4, eval = FALSE}
rs_plot <- rs_plot + theme(legend.position = "none")
rs_plot + rs_plot_2
```

```{r fig.height = 4}
